Liveness-Based Garbage Collection for Lazy Languages

### 2015-07-10 paper/paper.tex
Updated

Another advnatage of  this mixed garbage collection scheme  is that it
avoids the problem of multiple  explorations from the same cell.  This
is done by maintaining a flag in  each cell to indicate whether it was
copied using reachability.

@@

\section{Results}
%% \comment{To demonstrate the effectiveness of liveness-based garbage collection,
%% we  have  built a  prototype  consisting  of  an interpreter  for  our
%% language,  a  liveness  analyzer  and  a copying  collector  that  can
%% optionally use the results of liveness analysis for marking instead of
%% reachability. When the collector uses liveness for marking, we call it
%% a  {\em liveness-based  collector} (LGC),  else we  use the  term {\em
%%   reachability-based  collector}  (RGC).   The  copying  collector  is
%% neither incremental nor generational.  As a consequence, any cell that
%% becomes unreachable or  dead is assuredly collected in  the next round
%% of garbage collection.}

To test the utility of our method we have implemented a garbage-collector 
for a simple scheme-like first order language. It consists of an interpreter, 
liveness analyzer and a garbage-collector that can optionally use use reachability or liveness. 
Our benchmark consists of programs from nofib suite and some external programs manually converted to ANF.

>>>>

Another advantage of  this mixed garbage collection scheme  is that it
avoids the problem of multiple  explorations from the same cell.  This
is done by maintaining a flag in  each cell to indicate whether it was
copied using reachability.

@@

\section{Experimental evaluation}
%% \comment{To demonstrate the effectiveness of liveness-based garbage collection,
%% we  have  built a  prototype  consisting  of  an interpreter  for  our
%% language,  a  liveness  analyzer  and  a copying  collector  that  can
%% optionally use the results of liveness analysis for marking instead of
%% reachability. When the collector uses liveness for marking, we call it
%% a  {\em liveness-based  collector} (LGC),  else we  use the  term {\em
%%   reachability-based  collector}  (RGC).   The  copying  collector  is
%% neither incremental nor generational.  As a consequence, any cell that
%% becomes unreachable or  dead is assuredly collected in  the next round
%% of garbage collection.}

To   test  the   utility  of   our  method   we  have   implemented  a
garbage-collector for a simple scheme-like first order language having
non-strict semantics. It consists of an interpreter, liveness analyzer
and a  garbage-collector that can  optionally use  reachability or
liveness.  Our  benchmark consists  of programs  from nofib~\cite{nofib}  suite and
some external programs manually converted to ANF.
